Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1) \note{\scriptsize Authors, please add/check middle initials and affiliations}

### 2014-04-21 WSSSPE1_report/WSSSPE1_summary_report.tex
Fixes dashes that should be em-dashes.

Zentner et al.~\cite{Zentner_WSSSPE} describes experiences and challenges with the large
\toolname{nanoHUB.org} community, where community is defined as a ``body of persons of
common and especially professional interests scattered through a larger
society.'' Support is challenging because of the diversity of
viewpoints and needs. The group constantly examines its policies to determine
whether they are indirectly alienating part of the community or encouraging
particular types of use.
%
\toolname{nanoHUB}'s 10-year history with over 260,000 users annually provides a lot of
data to analyze. 4000 resources contributed by 1000 authors. \toolname{nanoHUB} serves
both the research and education community and the contribution model allows
researchers to get their codes out into the community and in use in education
very rapidly. The primary software challenges are twofold - support for the
\toolname{HUBzero} framework and challenges related to the software contributed by the
community.

@@

The paper points out 4 keys to sustaining the community: modular design,
growing a collaborative community, career paths and credit. In modular design,
the Cactus project went far beyond standard practices of APIs. Domain specific
languages (DSLs) allow decoupling of components - for example I/O, mesh
refinement, PAPI counters, and boundary conditions abstracted from science
code. In academia, publications are the main currency of credit. Because the
project connects code developments to science, the work is publishable and
modules are citable. Because of the open source, modular approach, programmers
can see the impact of their contributions and often continue work after
graduation. Career paths remain a challenge, however. Tasks that are essential
from a software engineering perspective are often not rewarded in academia. The
best programmers in a science environment often have multidisciplinary
expertise. This also is not rewarded in academia.

>>>>

Zentner et al.~\cite{Zentner_WSSSPE} describes experiences and challenges with the large
\toolname{nanoHUB.org} community, where community is defined as a ``body of persons of
common and especially professional interests scattered through a larger
society.'' Support is challenging because of the diversity of
viewpoints and needs. The group constantly examines its policies to determine
whether they are indirectly alienating part of the community or encouraging
particular types of use.
%
\toolname{nanoHUB}'s 10-year history with over 260,000 users annually provides a lot of
data to analyze. 4000 resources contributed by 1000 authors. \toolname{nanoHUB} serves
both the research and education community and the contribution model allows
researchers to get their codes out into the community and in use in education
very rapidly. The primary software challenges are twofold --- support for the
\toolname{HUBzero} framework and challenges related to the software contributed by the
community.

@@

The paper points out 4 keys to sustaining the community: modular design,
growing a collaborative community, career paths and credit. In modular design,
the Cactus project went far beyond standard practices of APIs. Domain specific
languages (DSLs) allow decoupling of components --- for example I/O, mesh
refinement, PAPI counters, and boundary conditions abstracted from science
code. In academia, publications are the main currency of credit. Because the
project connects code developments to science, the work is publishable and
modules are citable. Because of the open source, modular approach, programmers
can see the impact of their contributions and often continue work after
graduation. Career paths remain a challenge, however. Tasks that are essential
from a software engineering perspective are often not rewarded in academia. The
best programmers in a science environment often have multidisciplinary
expertise. This also is not rewarded in academia.
